---
title: "pH in Indian Lake Through Time"
author: "Andy Hasselwander"
date: "3/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(data.table)
library(plotly)
library(stringr)
```

#Load Acid Rain Data

```{r}
coordinates <- read.csv("LTM_Sample_Coordinates.csv")
coordinates <- coordinates[complete.cases(coordinates),]
colnames(coordinates) <- c("lat", "lng", "popup", "ALSC")
lakedata <- read.csv("LakeData.csv")
colnames(lakedata)[1] <- "confirmedDate"
lakedata$ALSC <- str_sub(lakedata$ALSC,2, str_length(lakedata$ALSC))
lakedata$confirmedDate <- as.Date(lakedata$confirmedDate, "%Y.%m.%d")
dateValues <- base::unique(lakedata$confirmedDate)
measurementValues <- colnames(lakedata)[8:ncol(lakedata)]
coordinates_and_data <- merge(coordinates, lakedata, by = "ALSC")
library(data.table)
coord_data_dt <- data.table(coordinates_and_data)
```

## Acid Rain in Indian Lake

Indian Lake is a man-made lake in the central region of the Adirondack park, in northern New York State. In the 1960s, coal power plants in the midwest dramatically increased their output of sulphur dioxide and other aerosols, that, when mixed with water droplets in the atmosphere, created sulphuric and other acids. These acids then fell with rain in the park, lowering pH. Starting in the 1990s, these plants began lowering their output of these aerosols, and pH has fallen in accordance.

```{r}

tsDF2 <- subset(coord_data_dt, 
                    popup == "INDIAN LAKE")
p <- plot_ly(tsDF2, x = ~confirmedDate, y = ~LABPH
             )
p

```
