---
title: "Acid Rain in the Adirondacks"
author: "Andy Hasselwander"
date: "March 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

```

## Acid Rain in the Adirondacks
Acid rain is created when coal plants in the midwest release sulpher dioxide (SO2) and nitrogen oxides into the atmosphere, where they are converted to sulphuric and nitric acids. These acids combine with water droplets to create acid rain. The Adirondack Long-Term Monitoring Program monitors lakes in the Adirondacks to understand the impact of acid rain, among other factors. This map the PH levels in monitored lakes. The data were collected by the Adirondack Lakes Survey Corporation, and are available at www.adirondacklakesurvey.org.

###Load coordinates and data, perform data scrubbing.

```{r}
coordinates <- read.csv("LTM_Sample_Coordinates.csv")
coordinates <- coordinates[complete.cases(coordinates),]
colnames(coordinates) <- c("lat", "lng", "popup", "ALSC")
lakedata <- read.csv("LakeData.csv")
colnames(lakedata)[1] <- "confirmedDate"
require(stringr)
lakedata$ALSC <- str_sub(lakedata$ALSC,2, str_length(lakedata$ALSC))

lakedata$confirmedDate <- as.Date(lakedata$confirmedDate, "%Y.%m.%d")
```

##Show Map of Lakes with Most Recent Acid Rain Data
This simple map shows the lake name, with the size of the circle representing pH levels. Red colors represent lower pH levels (more acidic.) This pulls the most recent data from September 2017. A future version will be interactive, allowing the user to select different collection dates and measurements.
```{r}

lakedataRecent <- lakedata[lakedata$confirmedDate == "2017-09-01",]

coordinates_and_data <- merge(coordinates, lakedataRecent, by = "ALSC")
require(RColorBrewer)
colors <- rev(brewer.pal(9, 'YlOrRd'))

acidColors <- cut(coordinates_and_data$LABPH, breaks = c(0,4,4.5,5,5.5,6,6.5,7,7.5,14), labels = colors)

require(leaflet)
latlon <- coordinates_and_data[,2:3] 
labels <- paste0(coordinates_and_data$popup, ", PH level = ", coordinates_and_data$LABPH, ", Date ", coordinates_and_data$confirmedDate)

adkLakes <- leaflet() 
latlon %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(popup=labels, color = acidColors, opacity = 1, clusterOptions = markerClusterOptions()) %>%
  addLegend(labels = c("pH < 4.0", "ph 4.0-4.5", "pH 4.5-5.0", "pH 5.0-5.5", "pH 5.5 - 6.0", "pH 6.0 - 6.5", "pH 6.5-7.0", "pH 7.0-7.5", "pH > 7.5"), colors = rev(brewer.pal(9, 'YlOrRd')))


```