---
title: "Acid Rain in the Adirondacks"
author: "Andy Hasselwander"
date: "March 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

```

## Acid Rain in the Adirondacks
Acid rain is creating when coal plants in the midwest release sulpher dioxide (SO2) and nitrogen oxides into the atmosphere, where it is converted into Sulphuric Acid. The Adirondack Long-Term Monitoring Program monitors these lakes for acid levels, as measured by pH. This map interactively displays the pH levels in monitored lakes. 

###Load coordinates and data

```{r}
coordinates <- read.csv("LTM_Sample_Coordinates.csv")
coordinates <- coordinates[complete.cases(coordinates),]
colnames(coordinates) <- c("lat", "lng", "popup", "ALSC")
lakedata <- read.csv("LakeData.csv")
colnames(lakedata)[1] <- "confirmedDate"
require(stringr)
lakedata$ALSC <- str_sub(lakedata$ALSC,2, str_length(lakedata$ALSC))

lakedata$confirmedDate <- as.Date(lakedata$confirmedDate, "%Y.%m.%d")
```

##Show Map of Lakes with Most Recent Acid Rain Data
This simple map shows the lake name, with the size of the circle representing acid levels. This pulls the most recent data from September 2017.
```{r}

lakedataRecent <- lakedata[lakedata$confirmedDate == "2017-09-01",]

coordinates_and_data <- merge(coordinates, lakedataRecent, by = "ALSC")

require(leaflet)
latlon <- coordinates_and_data[,2:3] 
labels <- paste0(coordinates_and_data$popup, ", SO4 level = ", coordinates_and_data$SO4)

adkLakes <- leaflet() 
latlon %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight =1, popup=labels, radius = coordinates_and_data$SO4 * 500)


```